Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology

### 2019-09-09 reproducing_registered_reports.Rmd
changes through line 105

Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the articles. @hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal *Cognition*. Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance. The authors estimated that it took between 2-25 hours to reproduce the reported results per article, but they did not record the exact time. @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals. They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one paper's results could not be reproduced due to a lack of a software license, and 16 articles' findings could not be reproduced with access to the required software. For the remaining articles, 32 sets of results could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results. @stodden_empirical_2018 analyzed data availability in the journal *Science* in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors. For all datasets they acquired after e-mailing authors for data and code, 26% was estimated to be computationally reproducible. These studies reveal that there is clear room for improvement in how reproducible published articles are.

We set out to examine the data availability and reproducibility in Registered Reports published in psychological science. Our main interest was to examine the computational reproducibility of the main analyses reported in published articles, without contacting the original authors. One of the main benefits of sharing data and code with an article (compared to making these files available upon request) is that results can be reproduced, and data reused even if the original author can no longer be reached.

@@

Our main objective was to examine how reusable data and code underlying Registered Reports are, based purely on the information provided in the published literature. We examined how many authors voluntarily shared data and code, and the extent to which we could reproduce reported analyses without contacting the original authors. While reproducing the results reported in Registered Reports, we kept track of factors that facilitated reproducibility or that made reproducing the result more difficult. We report these qualitative findings with an aim to highlight how current practices can be improved.

@@

To find Registered Reports published in psychology we drew from a database of registered reports maintained by the Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018]. Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left `r length(all_data$doi)` studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of `r sum(all_data$included_language == FALSE, na.rm = TRUE)` additional study.

>>>>

Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the articles. @hardwicke_data_2018 examined the reproducibility of 35 articles published in the journal *Cognition*. Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance. The authors estimated that it took between 2-25 hours to reproduce the reported results per article, but they did not record the exact time. @stockemer_data_2018 analyzed reproducibility in all articles published in 2015 in three political science journals. They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one paper's results could not be reproduced due to a lack of a software license, and 16 articles' findings could not be reproduced with access to the required software. For the remaining articles, 32 sets of results could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results. @stodden_empirical_2018 analyzed data availability in the journal *Science* in 2011-2012 and found that 26 of 204 (or 13%) of articles provided information to retrieve data and/or code without contacting the authors. For all datasets they acquired after e-mailing authors for data and code, 26% were estimated to be computationally reproducible. These studies reveal that there is clear room for improvement in how reproducible published articles are.

We set out to examine the data availability and reproducibility in Registered Reports published in psychological science. Our main interest was to examine the computational reproducibility of the main analyses reported in published articles, without contacting the original authors. One of the main benefits of sharing data and code alongside an article (compared to making these files available upon request) is that results can be reproduced, and data reused even if the original author can no longer be reached.

@@

Our main objective was to examine how reusable data and code underlying Registered Reports are, based solely on the information provided in those articles. We examined how many authors voluntarily shared data and code, and the extent to which we could reproduce reported analyses without contacting the original authors. While reproducing the results reported in Registered Reports, we kept track of factors that facilitated reproducibility or that made reproducing results more difficult. We report these qualitative findings with an aim to highlight how current practices can be improved.

@@

To find Registered Reports published in psychology we drew from a database of registered reports maintained by the Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018]. Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left `r length(all_data$doi)` studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of one additional study.

### 2019-09-09 reproducing_registered_reports.tex
changes through line 105

Researchers are currently exploring ways to make science more open and transparent. Among novel developments such as pre-registration, pre-prints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., (Morey et al., 2016). Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work. This requires the development of new skills and best practices, since most scientists have not received training in how to make their work reproducible. It is important to evaluate how data and code are currently being shared, and how easy it is to reproduce analyses reported in the published literature, to learn what can be improved. With this goal in mind, we computationally reproduced the main results of Registered Reports published in the psychological literature.

It is desirable that research is reproducible. Data availability has the potential to make science more efficient by facilitating the re-use of data. The availability of analysis code makes it possible for peers to check and correct published findings. According to Kitzes, Turek, and Deniz (2017), computational reproducibility means that ''a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.'' For scientific research to be computationally reproducible, the data and code needs to be shared.

@@

Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the published article. Hardwicke et al. (2018) examined the reproducibility of 35 articles published in the journal \emph{Cognition}. Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance. The authors estimated that it took between 2-25 hours to reproduce the reported results per article, but they did not record the exact time. Stockemer, Koehler, and Lentz (2018) analyzed reproducibility in all articles published in 2015 in three political science journals. They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one could not be reproduced due to a lack of a software license, and 16 articles could not be reproduced with access to the required software. For the remaining articles, 32 could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results. Stodden, Seiler, and Ma (2018) analyzed data availability in the journal \emph{Science} in 2011-2012 and found that 26 of 204 (or 13\%) of articles provided information to retrieve data and/or code without contacting the authors. For all datasets they acquired after e-mailing authors for data and code, 26\% was estimated to be computationally reproducible. These studies reveal that there is clear room for improvement in how reproducible published articles are.

We set out to examine the data availability and reproducibility in Registered Reports published in psychological science. Our main interest was to examine the computational reproducibility of the main analyses reported in published articles, without contacting the original authors. One of the main benefits of sharing data and code with an article (compared to making these files available upon request) is that results can be reproduced, and data reused even if the original author can no longer be reached.

@@

To find Registered Reports published in psychology we drew from a database of registered reports maintained by the Center for Open Science.\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports (Hagger et al., 2016) and Many Labs projects (Klein et al., 2014, 2018). Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left 62 studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of 1 additional study.

>>>>

Researchers are currently exploring ways to make science more open and transparent. Among novel developments such as pre-registration, preprints, and open peer review, an increasing number of journals, funders, and researchers are beginning to expect that data, materials, and analysis code will be shared by default with scientific publications (e.g., (Morey et al., 2016). Sharing data and analysis code with scientific publications allows others to more easily reproduce, check, and build on existing work. This requires the development of new skills and best practices, since most scientists have not received training in how to make their work reproducible. It is important to evaluate how data and code are currently being shared, and how easy it is to reproduce analyses reported in the published literature, to learn what can be improved. With this goal in mind, we computationally reproduced the main results of Registered Reports published in the psychological literature.

It is desirable that research is reproducible. Data availability has the potential to make science more efficient by facilitating the re-use of data. The availability of analysis code makes it possible for peers to check and correct published findings. According to Kitzes, Turek, and Deniz (2017), computational reproducibility means that ''a second investigator (including the original researcher in the future) can recreate the final reported results of the project, including key quantitative findings, tables, and figures, given only a set of files and written instructions.'' For scientific research to be computationally reproducible, the data and code need to be shared.

@@

Recently, scholars have started to empirically examine the extent to which data is shared with published articles, and, if so, whether it was possible to reproduce the data analysis reported in the articles. Hardwicke et al. (2018) examined the reproducibility of 35 articles published in the journal \emph{Cognition}. Eleven articles could be reproduced without assistance from the original authors, and 13 articles contained at least one outcome that could not be reproduced even with author assistance. The authors estimated that it took between 2-25 hours to reproduce the reported results per article, but they did not record the exact time. Stockemer, Koehler, and Lentz (2018) analyzed reproducibility in all articles published in 2015 in three political science journals. They emailed authors for the code and data, and found that for 71 articles for which they received code and data, one paper's results could not be reproduced due to a lack of a software license, and 16 articles' findings could not be reproduced with access to the required software. For the remaining articles, 32 sets of results could be exactly reproduced, 19 could be reproduced with slight differences, and 3 articles yielded significantly different results. Stodden, Seiler, and Ma (2018) analyzed data availability in the journal \emph{Science} in 2011-2012 and found that 26 of 204 (or 13\%) of articles provided information to retrieve data and/or code without contacting the authors. For all datasets they acquired after e-mailing authors for data and code, 26\% were estimated to be computationally reproducible. These studies reveal that there is clear room for improvement in how reproducible published articles are.

We set out to examine the data availability and reproducibility in Registered Reports published in psychological science. Our main interest was to examine the computational reproducibility of the main analyses reported in published articles, without contacting the original authors. One of the main benefits of sharing data and code alongside an article (compared to making these files available upon request) is that results can be reproduced, and data reused even if the original author can no longer be reached.

@@

To find Registered Reports published in psychology we drew from a database of registered reports maintained by the Center for Open Science.\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports (Hagger et al., 2016) and Many Labs projects (Klein et al., 2014, 2018). Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left 62 studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of one additional study.
